Model exploration

### 2015-07-01 documentation/model_exploration.Rmd
update model exploration

```{r, echo=FALSE}
# ODE solving
library("deSolve")

@@

workstation <-  list(host = "162.38.184.118", user = "schneider",
                     rscript = "/usr/lib/R/bin/Rscript",
                     snowlib = "/usr/lib/R/library")

workerlist <- c(rep("localhost", times = 10))

@@

```{r, echo=FALSE, fig.height = 6}
colpal <- list(mort = c("#000000","#00000040","#00000030","#00000020"), grow = c("#009933","#00993340","#00993330","#00993320") )
rho <- seq(0,1,length = 100)
parms <- defparms

@@

```{r, echo = FALSE, fig.cap="a) mean field approximation of density dependent mortality and growth of vegetation with local facilitation. As plant cover increases, the effect of facilitation is stronger. solid points show steady states, open circle shows unstable equilibrium. b) bifurcation diagram of vegetation cover over a gradient of environmental quality (black: steady states, grey: unstable equilibria). High facilitation has strong stabilising effects on the vegetated state. "}

@@

```{r, echo = FALSE}

>>>>

```{r, echo=FALSE, warning=FALSE}
# ODE solving
library("deSolve")

@@

workstation <-  list(host = "162.38.184.118", user = "florian",
                     rscript = "/usr/lib/R/bin/Rscript",
                     snowlib = "/usr/lib/R/library")

workerlist <- c(rep("localhost", times = 7))

@@

```{r, echo=FALSE, fig.height = 6, warning=FALSE}
colpal <- list(mort = c("#000000","#00000040","#00000030","#00000020"), grow = c("#009933","#00993340","#00993330","#00993320") )
rho <- seq(0,1,length = 100)
parms <- defparms

@@

```{r, echo = FALSE, fig.cap="a) mean field approximation of density dependent mortality and growth of vegetation with local facilitation. As plant cover increases, the effect of facilitation is stronger. solid points show steady states, open circle shows unstable equilibrium. b) bifurcation diagram of vegetation cover over a gradient of environmental quality (black: steady states, grey: unstable equilibria). High facilitation has strong stabilising effects on the vegetated state. ", warning=FALSE}

@@

```{r, echo = FALSE, warning=FALSE}
